Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Distributed bits are better in abstracte

\begin{abstract}
  In the online Graph RePartitioning problem, we are given a sequence of pairwise communication requests between n nodes, revealed online.
  The objective is to service these requests by partitioning the nodes into $\ell$ clusters, each of size $k$, such that frequently communicating nodes are located in the same cluster.
  The partitioning can be updated by migrating nodes between clusters for a fixed cost.
  The goal is to jointly minimize the amount of inter-cluster communication and migration cost.

@@

\section{Introduction}
Distributed   applications,  including  batch  processing, streaming, and scale-out databases generate a significant amount of network traffic and a~considerable fraction of their runtime is due to network activity. In this  paper, we study  algorithms  for collocating frequently communicating nodes in a distributed networked systems in an online fashion.

>>>>

\begin{abstract}
  Distributed   applications,  including  batch  processing, streaming, and scale-out databases generate a significant amount of network traffic and a~considerable fraction of their runtime is due to network activity. In this  paper, we study  algorithms  for collocating frequently communicating nodes in a distributed networked systems in an online fashion.

  In the online Graph RePartitioning problem, we are given a sequence of pairwise communication requests between n nodes, revealed online.
  The objective is to service these requests by partitioning the nodes into $\ell$ clusters, each of size $k$, such that frequently communicating nodes are located in the same cluster.
  The partitioning can be updated by migrating nodes between clusters for a fixed cost.
  The goal is to jointly minimize the amount of inter-cluster communication and migration cost.

@@

\section{Introduction}
